Rank Verification for Exponential Families

### 2016-09-28 verifying-winner.tex
two bibs combined, elaborated on lemma

\begin{proof}
We can prove so with a coupling argument: for any sequence $x_1, x_2, \ldots, x_n$, define $y_1, y_2, \ldots, y_n$, obtained by swapping $x_1$ with the largest value in the sequence $x$. Hence
$$\exp\left(\theta_1 y_1 + \theta_2 y_2 + \cdots + \theta_n y_n - \psi\left(\theta\right)\right) g\left(X\right) \ge \exp\left(\theta_1 x_1 + \theta_2 x_2 + \cdots + \theta_n x_n - \psi\left(\theta\right)\right) g\left(X\right).$$
Integrating both sides over $\mathbb{R}^n$ (or $\mathbb{Z}^n$ in the case of counting measure) gives
$$n \PP\left[1 \text{ wins}\right] \ge 1$$
as desired. \WFcomment{can you make this argument a bit more explicit? And how does it work for discrete data?}
\end{proof}

@@

\bibliographystyle{plainnat}
\bibliography{papers,additional}

>>>>

\begin{proof}
We can prove so with a coupling argument: for any sequence $x_1, x_2, \ldots, x_n$, define $\tau\left(x\right) = \left\{\tau\left(x_j\right)\right\}_{j = 1, \ldots, n}$, obtained by swapping $x_1$ with the largest value in the sequence $x$. Hence
$$\exp\left(\theta_1 \tau\left(x_1\right) + \cdots + \theta_n \tau\left(x_n\right) - \psi\left(\theta\right)\right) g\left(X\right) \ge \exp\left(\theta_1 x_1 + \cdots + \theta_n x_n - \psi\left(\theta\right)\right) g\left(X\right).$$
If we integrating both sides over $\mathbb{R}^n$ (or $\mathbb{Z}^n$ in the case of counting measure), the right hand side gives $1$. Since $\tau$ is an $n$-to-$1$ mapping, the left hand side is $n$ times the integral over $\left\{x_1 \ge \max_{j > 1} x_j\right\}$. In other words
$$n \PP\left[1 \text{ wins}\right] \ge 1$$
as desired.

In the case of counting measure, the above argument follows if a subscript is attached to identical observations uniformly to ensure strict ordering.
\end{proof}

@@

\bibliographystyle{plainnat}
\bibliography{papers}
